A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end Training

### 2016-08-02 paper.tex
minor fixes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{We expect to release the set before the camera-ready deadline.}

@@

The CF worker playing the role of the client is asked to request specific information from the operator – a goal.
They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.
% \footnote{We expect to release the set before the camera-ready deadline.}

@@

The CF worker playing the role of the client is asked to request specific information from the operator – a goal.
They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
For example, the client may at first attempts to find a restaurant serving Chinese food, but later change their mind and seeks British food.
